---
title: "Part II excercise 1"
author: "Zahida"
date: "9/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **R Markdown Cache Example**

This example shows that by using Cache= True while doing calculations for a specific object e.g X(in this case), changing the object value changes the results if we use the "dependson"function otherwise selecting cache as T will store the assigned value of the object and everytime this will give a misleading value


```{r X, cache=TRUE}
X = 10
```


```{r, cache=TRUE}
(Y =  2*X)
```

```{r, cache = TRUE, dependson = "X"}
(Y = 2*X)
```
# **Standard Normal Distribution simulating 100 Random samples**

```{r,Simulation}
x<-rnorm(100)
x




```
# **Median**

```{r,Computemedianx }
median(x)
```
# **Mean**

```{r, mean}
mean(x)

```

# **Variance**
```{r, variance}
var(x)
```

# **Histogram**
```{r, graph}
hist(x)
```
# **Results**
These results are different from expected results because this is random distribution of random samples.

```{r}
```
 $$y = X\mathbf{\beta} + \epsilon$$

$$\mathbf{A} := \left[a_{i,j}\right]_{i,j = 1, \ldots, p}$$

<font color ="blue">“Keep calm and carry on programming" </font>

<button data-toggle="collapse" data-target="#demo">See more</button>
<div id="demo" class="collapse">
Not much more to see
</div>

<div class="alert alert-success">
  <strong>Forza Roma:</strong> sempre
</div>

